EP1162_Prelim_Data_Screening

### 2020-02-28 data-raw/ep1162_prelimDataScreening.Rmd
Data cleaning

---
title: "EP1162_Prelim_Data_Screening"
author: "Hardy Griesbauer"
date: "18/02/2020"
output:
  word_document: default
  html_document: default
---

@@

In total, there are `r dbhDecrease %>% count(TreeID) %>% nrow()` trees with this situation.  I have the treeID saved and can provide them if we want to double check these trees.

@@

One thing to note: the following trees had fallen as of 2019, which means we should not interpolate their 2019 values:
```{r}
dbhDecrease %>% 
  filter(Year==2019 & is.na(DBH))

dbhEdit2<-
  readr::read_csv(here::here("data-raw","dbh_for_edit.csv"))

@@

# Interpolation
dbhEdit3<-
  dbhEdit2 %>% 
  pivot_longer(cols=`1992`:`2019`,names_to="Year",values_to="DBH") %>% 
  mutate(DBH=as.numeric(DBH)) %>% 
  mutate(Year=paste("01-01",Year,sep="-")) %>% 
  mutate(Year=dmy(Year)) %>% 
  mutate(TreeID=factor(TreeID)) %>% 
  group_by(TreeID) %>% 
  pad() %>% 
  ungroup() %>% 
  mutate(Year=year(Year)) %>% 
  as.data.frame()

@@

x<-
  dbhPred %>% 
  drop_na(DBH)

 mono.x<- by(x$DBH,x$TreeID,monotonic)

@@

  dbhPred[dbhPred$TreeID==31 & dbhPred$Year==1994,"DBH"]=22.5

@@

*The chunk below isn't set to run, because we only want to do this once*

```{r eval=FALSE}
x<-
  dat %>% 
  drop_na(Height) %>% # drop rows with missing Height values 
  arrange(Plot,TreeID,Year) %>% 
  mutate(id=paste(Plot,TreeID,sep="."))

>>>>

---
title: "EP1162_Prelim_Data_Screening"
author: "Hardy Griesbauer"
date: "18/02/2020"
output:
  html_document: default
  word_document: default
---

@@

In total, there are `r dbhDecrease %>% count(TreeID) %>% nrow()` trees with this situation.

@@

One thing to note: the following trees had fallen as of 2019, which means we should not interpolate their 2019 values:

```{r}
dbhDecrease %>% 
  filter(Year==2019 & is.na(DBH))
```

*The following chunk won't run, because we only want to do this once*
```{r eval=FALSE}
dbhEdit2<-
  readr::read_csv(here::here("data-raw","dbh_for_edit.csv"))

@@

# Interpolation
dbhEdit3<-
  dbhEdit2 %>% 
  pivot_longer(cols=`1992`:`2019`,names_to="Year",values_to="DBH") %>% 
  mutate(DBH=as.numeric(DBH)) %>% 
  mutate(Year=paste("01-01",Year,sep="-")) %>% 
  mutate(Year=dmy(Year)) %>% 
  mutate(TreeID=factor(TreeID)) %>% 
  group_by(TreeID) %>% 
  pad() %>% # pad out time series so we can interpolate
  ungroup() %>% 
  mutate(Year=year(Year)) %>% 
  as.data.frame()

@@

x<-
  dbhPred %>% 
  drop_na(DBH.Pred)

 mono.x<- by(x$DBH.Pred,x$TreeID,monotonic)

@@

  dbhPred[dbhPred$TreeID==31 & dbhPred$Year==1994,"DBH.Pred"]=22.5

@@

```{r}
x<-
  dat %>% 
  drop_na(Height) %>% # drop rows with missing Height values 
  arrange(Plot,TreeID,Year) %>% 
  mutate(id=paste(Plot,TreeID,sep="."))
